Optimal recommender system with strategic alternatives \\ Term Paper

### 2020-01-16 Draft.tex
Draft

\documentclass[a4paper]{article}
\usepackage[12pt]{extsizes} % 
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage{setspace,amsmath}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage{titlesec}
\usepackage{pdfpages}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{angles,quotes}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{breakcites}
\usepackage[makeroom]{cancel}
\usepackage{mathrsfs} % 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\addto\captionsrussian{\renewcommand{\figurename}{Fig.}}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{}
{\hbox{$\mathsurround=0pt #1$}}{}}
\usepackage{graphicx}  % 
\graphicspath{{images/}{images2/}}  % 
\setlength\fboxsep{3pt} %  \fbox{} 
\setlength\fboxrule{1pt} % \fbox{}
\usepackage{wrapfig} % 
\newcommand{\prob}{\mathbb{P}}
\newcommand{\norma}{\mathcal{N}}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\summa}{\sum_{i=1}^n}
\usepackage[left=15mm, top=20mm, right=15mm, bottom=20mm, nohead, footskip=10mm]{geometry} % 
\usepackage{tikz} % 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{definition}[theorem]{Definition}
\title{Optimal recommender system with strategic alternatives \\ Market Design. Term Project}
\date{}
\author{Danil Fedchenko}
\begin{document} % 
	\maketitle
	\section{Introduction}
	Suppose you came to New-York and would like to find a good restaurant to go out tonight. Or you are going to spend your upcoming vacation on the coast of Spain and you need to find a hotel. What would you do? Where would you search for?  Before the World Wide Web, people in such cases relied upon guide-books and brochures distributed by traveling agents. Those guides usually quickly became out-of-dated and were criticized for containing a misleading information.

@@

	Finally, Papanstasiou et al. \cite{papanastasiou2017} extended ideas developed in \cite{kremer2014} and \cite{che2015}, and build a dynamic, stochastic model. In their model, agents also arrive sequentially to the platform and should choose between two alternatives that generate stochastically exogenous payoff. The platform in the paper designs a recommendation policy. Although the optimal policy turns out to have a complicated form, authors demonstrate that in this case the full revelation policy is not the best one, and the optimal policy involves information obfuscation.

@@

 	\begin{assumption}
 		If the good is not recommended to the customer, then the customer does not consume it. While if the good is recommended the customer may or may not choose it.
 	\end{assumption}
 	This assumption implies that without the platform the customer is unable to find the good. Think about \textit{TripAdvisor}, if it does not show you a restaurant, you will not know about the existence of this restaurant. At the same time, if \textit{TripAdvisor} shows you an option it is up to you whether to go there or not.
 	\begin{assumption}
 		The utility customers obtain in the bad state, $q > 0$ and hence it is always profitable for the platform to recommend the good to at least a small share of customers.
 	\end{assumption}
 This assumption ensures that the platform can get the information about the state of the firm each period.
 \begin{assumption}
 	$p \ge 0.5$
 \end{assumption}
This assumption, on one hand, is pure technical, and simplifies an analysis of optimal policy, but on the other hand it seems reasonable that once the firm invests, the probability that investment will lead to an increase in quality is at least 50\%.
\section{Analysis}
Although the recommender policy the platform employs can be a complicated function of all previous states, I start the analysis from the simplest policy. Namely, I firstly consider the policy that takes into account only the previous realization of the quality of the good.
\subsection{One-round recommendation policy}
Suppose that the platform employs the recommender policy that is based only on the previous period realization of the quality of the good. In this case the policy consists of two shares $\{s^0, s^1\}$ such that $$s_t = \begin{cases}
s^0, \text{ if }\mathcal{Q}_{t-1} = b\\
s^1, \text{ if }\mathcal{Q}_{t-1} = g
\end{cases}$$
The platform should choose $s^0, s^1$ to maximize its objective taking into account incentives of the firm. But firstly as a benchmark consider the first-best case, when the firm always invest. In this case the recommender policy is characterized by the following lemma

@@

	The firm exerts effort at bad state if and only if $$\delta V_{bb} \le \delta p V_{gb} + \delta (1-p)V_{bb} - c \iff V_{gb} - V_{bb} \ge \frac{c}{\delta p}$$
	Similarly, the firm exerts effort at good state if and only if $$V_{gg} - V_{bg} \ge \frac{c}{\delta p}$$ Suppose that the firm exerts effort at bad state, by way of contradiction assume that the firm does not invest at good state. In this case the system of equation becomes
	$$	\begin{cases}
	V_{bb} = \mathcal{P}s^0 + \delta p V_{gb} + \delta (1-p)V_{bb} - c\\
	V_{bg} = \mathcal{P}s^1 + \delta p V_{gb} + \delta (1-p)V_{bb} - c\\
	V_{gb} = \mathcal{P}s^0 + \delta V_{bg}\\
	V_{gg} = \mathcal{P}s^1 + \delta V_{bg}
	\end{cases}$$ and the solution is $$\begin{cases}
	V_{bb} = \frac{1+\delta p - \delta^2p}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 + \frac{\delta^2 p}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c}{(1-\delta)(1+\delta p)}\\
	V_{bg} = \frac{\delta}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 + \frac{1-\delta + \delta p}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c}{(1-\delta)(1+\delta p)}\\
	V_{gb} = \frac{(1+\delta p)(1-\delta)+\delta^2}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 - \frac{\delta^2(1-p)}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c \delta}{(1-\delta)(1+\delta p)}\\
	V_{gg} = \frac{\delta^2}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 + \frac{1 - \delta^2 + \delta p}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c\delta}{(1-\delta)(1+\delta p)}
	\end{cases}$$
	the condition that the firm invest at bad state is
	$$V_{gb} - V_{bb} = \frac{\delta\mathcal{P}}{1+\delta p}(s^1 - s^0) + \frac{c}{1+\delta p} \ge \frac{c}{\delta p}$$
	But this implies
	$$\frac{c}{\delta p} \le \frac{\delta\mathcal{P}}{1 + \delta p}(s^1 - s^0) + \frac{c}{1 + \delta p} = V_{gg} - V_{bg}$$ and hence it is also optimal to invest at good state. The contradiction demonstrates that if the firm invests at the bad state, it also invest at a good state. Using the similar argument it can be shown that investing at the good state also must imply investment at the bad state.
\end{proof}
The result means that either the firm invests at both states or does not invest at all.
The next proposition characterize the policy that induce the firm to invest in quality.
\begin{proposition}\label{prop1}
	Given the recommender policy $\{s^0, s^1\}$, the firm exerts effort at both states if and only if $$s^1 - s^0 \ge \frac{c}{\delta^2 p}$$
\end{proposition}
\begin{proof}
	Suppose the firm does not invest at all, in this case the system \eqref{eq1} becomes
	\begin{align*}
	\begin{cases}
	V_{bb} = \mathcal{P}s^0 + \delta V_{bb}\\
	V_{bg} = \mathcal{P}s^1 + \delta V_{bb}\\
	V_{gb} = \mathcal{P}s^0 + \delta V_{bg}\\
	V_{gg} = \mathcal{P}s^1 + \delta V_{bg}
	\end{cases} \to \begin{cases}
	V_{bb} = \frac{\mathcal{P}s^0}{1-\delta}\\
	V_{bg} = \mathcal{P}s^1 +\frac{\delta}{1-\delta}s^0\\
	V_{gb} = \delta \mathcal{P}s^1 + \frac{1-\delta + \delta^2}{1-\delta}\mathcal{P}s^0\\
	V_{gg} = (1+\delta)\mathcal{P}s^1 + \frac{\delta^2}{1-\delta}\mathcal{P}s^0
	\end{cases}
	\end{align*}
	The necessary condition that ensures that the firm does not invest is $	V_{gb} - V_{bb} < \frac{c}{\delta p}$. Here, $$	V_{gb} - V_{bb} = \delta \mathcal{P}(s^1 - s^0)$$ Hence, the firm will not invest if $s^1 - s^0 < \frac{c}{\delta^2 p \mathcal{P}}$.

	Now suppose, the firm invests in both states. In this case the system \eqref{eq1} becomes
	\begin{align*}
	\begin{cases}
	V_{bb} = \mathcal{P}s^0 + \delta p V_{gb} + \delta(1-p)V_{bb} - c\\
	V_{bg} = \mathcal{P}s^1 + \delta p V_{gb} + \delta(1-p)V_{bb} - c\\
	V_{gb} = \mathcal{P}s^0 + \delta pV_{gg} + \delta(1-p)V_{bg} - c\\
	V_{gg} = \mathcal{P}s^1 + \delta p V_{gg} + \delta (1 - p)V_{bg} - c
	\end{cases}
	\end{align*}
	It is a system of linear equations, and its solution is given by:
	$$\begin{cases}
	V_{bb} = \frac{\delta^2p}{1-\delta}\mathcal{P}s^1 + \frac{1-\delta^2p}{1-\delta}\mathcal{P}s^0 - \frac{c}{1-\delta}\\
	V_{bg} = \frac{1-\delta + \delta^2p}{1-\delta}\mathcal{P}s^1 + \frac{\delta(1-\delta p)}{1-\delta}\mathcal{P}s^0 - \frac{c}{1-\delta}\\
	V_{gb} = \frac{\delta(1-\delta+\delta p)}{1-\delta}\mathcal{P}s^1 + \frac{1-\delta + \delta^2 - \delta^2 p}{1- \delta}\mathcal{P}s^0 - \frac{c}{1-\delta}\\
	V_{gg} = \frac{1 - \delta^2 + \delta^2 p}{1 - \delta}\mathcal{P}s^1 + \frac{\delta^2(1-p)}{1- \delta}\mathcal{P}s^0 - \frac{c}{1 - \delta}
	\end{cases}$$
	and again to ensure that the firm indeed invests one needs to check that $V_{gb} - V_{bb} \ge \frac{c}{\delta p}$. In this case $$V_{gb} - V_{bb} = \delta\mathcal{P}(s^1 - s^0) \ge \frac{c}{\delta p} \iff s^1 - s^0 \ge \frac{c}{\delta^2 p \mathcal{P}}$$
\end{proof}
The result means that the difference in demand of customers that the platform provides the firm with should be high enough to make it optimal for the firm to invest in quality. Also, the straightforward corollary can be obtained
\begin{corollary}
	It becomes harder to encourage firm to invest if either cost of investment $c$ is high, or the probability that investment results in quality increase $p$ is low, or the discount factor $\delta$ is low, ot the priced paid by customers $\mathcal{P}$ is low.
\end{corollary}

The next step is to choose the policy $\{s^0, s^1\}$ to maximize the platform's utility subject to the constraint imposed by the Proposition \ref{prop1}. The following theorem characterize the optimal one-round recommender policy.
\begin{theorem}
	If it is optimal to encourage the firm to invest, then the optimal one-round recommender policy is characterized by $$s^1 = \min \left\{ p + q(1-p) - \mathcal{P} + \frac{c}{\delta^2 p \mathcal{P}} - \frac{c}{\delta \mathcal{P}}, 1\right\}, s^0 = \max\left\{ p + q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}}, 0\right\}$$
\end{theorem} 
\begin{proof}
	Let $U_i$ be the expected discounted value of the platform if the state of the firm in the previous period was $i$. Then these values are solutions to the following system of equations. 
	\begin{align*}
	&\begin{cases}
	U_b = p\left((1-\mathcal{P})s^0 - \frac{(s^0)^2}{2} + \delta U_g\right) + (1-p)\left((q - \mathcal{P})s^0 - \frac{(s^0)^2}{2} + \delta U_b \right)\\
	U_g = p\left((1- \mathcal{P})s^1 - \frac{(s^1)^2}{2} + \delta U_g\right) + (1-p)\left((q - \mathcal{P})s^1 - \frac{(s^1)^2}{2} + \delta U_b \right)
	\end{cases} 
	\end{align*}
	which can be rewritten as
	\begin{align*}
	\begin{cases}
	U_b = \frac{1}{1 - \delta(1-p)} \left( (p + (1-p)q - \mathcal{P})s^0 - \frac{(s^0)^2}{2} \right) + \frac{p\delta}{1 - \delta(1-p)}U_g\\
	U_g = \frac{1}{1 - \delta p} \left( (p + (1-p)q - \mathcal{P})s^1 - \frac{(s^1)^2}{2} \right) + \frac{(1-p)\delta}{1 - \delta p}U_b
	\end{cases}
	\end{align*}
	the solution is given by
	$$\begin{cases}
	U_b = \frac{1-\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^0 - \frac{(s^0)^2}{2}\right) + \frac{\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^1 - \frac{(s^1)^2}{2}\right)\\
	U_g = \frac{\delta (1-p)}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^0 - \frac{(s^0)^2}{2}\right) +\frac{1-\delta(1- p)}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^1 - \frac{(s^1)^2}{2}\right)
	\end{cases}$$
	without loss of generality suppose that at $t = 0$ the firm is at bad state and the platform knows it. Then the platform should solve the following problem
	\begin{align*}
	\underset{s^1, s^0}{\max}&\ \frac{1-\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^0 - \frac{(s^0)^2}{2}\right) + \frac{\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^1 - \frac{(s^1)^2}{2}\right)
	\end{align*}
	Clearly $s^1 - s^0 \ge \frac{c}{\delta^2 p \mathcal{P}}$ should bind. Suppose that $s^1 < 1$, we can plug $s^0 = s^1 - \frac{c}{\delta^2 p \mathcal{P}}$ into the objective function. In this case the optimal solution is given by \begin{align}\label{eq2}
	s^0 &= p + q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} \nonumber\\
	s^1 &= p + q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}}
	\end{align}
	We should consider the case $s^1 = 1$, however if $s^1$ obtained in \eqref{eq2} is less than 1, then in case $p \ge 0.5$ it can be shown that the platform's profit is greater for this $s^1$, comparing to $s^1 = 1$.
\end{proof}
As we can see, the optimal one-round recommender policy with the strategic firm differs from the first-best policy when the firm is not strategic. With strategic firm the platform has to "punish" and "reward" the firm by decreasing and increasing the recommended share comparing to the first-best case. Namely, $s^0_{FB} - s^0 = \frac{c}{\delta \mathcal{P}}$, so the amount of punishment decreases once $\delta \to 1$ or $\mathcal{P} \to 1$, and increases once $c \to 1$. Note that if $q > 1 - \frac{c}{\delta p \mathcal{P}} - \frac{\mathcal{P}}{p}$ then $s^0 < q$ which means that the share of customers $q - s^0$ who for sure could derive positive utility from using the good are not recommended doing so. This may suggest that it is not always optimal to induce the firm to invest in quality.

In addition, the recommender policy above is clearly not incentive compatible: those customers whose outside option $r_i \in \left(p+q(1-p) - \mathcal{P}, s^1 \right)$ would rather choose the outside option than follow the recommendation. This is because by following recommendation, given that the firm is investing in quality, the expected utility of the customer is $p + q(1-p) - \mathcal{P}$ while the outside option yields more. But that means that the platform cannot induce the firm to invest in quality since the firm does not obtain enough profit. That is why, the optimal one-round recommender policy with strategic customers should be different from that obtained in this section.

>>>>

\documentclass[a4paper]{article}
\usepackage[12pt]{extsizes} % 
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage{setspace,amsmath}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage{titlesec}
\usepackage{pdfpages}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{angles,quotes}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{breakcites}
\usepackage[makeroom]{cancel}
\usepackage{mathrsfs} % 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\addto\captionsrussian{\renewcommand{\figurename}{Fig.}}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{}
{\hbox{$\mathsurround=0pt #1$}}{}}
\usepackage{graphicx}  % 
\graphicspath{{images/}{images2/}}  % 
\setlength\fboxsep{3pt} %  \fbox{} 
\setlength\fboxrule{1pt} % \fbox{}
\usepackage{wrapfig} % 
%\newenvironment{abstract}[0]{\small\rm
%	\begin{center}ABSTRACT
%		\\ \vspace{8pt}
%		\begin{minipage}{5.2in}\smalllineskip
%			\hspace{1pc}}{\end{minipage}\end{center}\vspace{-1pt}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\norma}{\mathcal{N}}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\summa}{\sum_{i=1}^n}
\usepackage[left=15mm, top=20mm, right=15mm, bottom=20mm, nohead, footskip=10mm]{geometry} % 
\usepackage{tikz} % 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{definition}[theorem]{Definition}
\title{Optimal recommender system with strategic alternatives \\ Term Paper}
\date{}
\author{Danil Fedchenko}
\begin{document} % 
	\maketitle
	\begin{abstract}
		Recommender systems became an integral part of our lives. Many papers studied the design of an optimal system that can balance exploration and exploitation for the myopic short-living agents. In previous works, the quality of alternatives (the utility customers derive upon consuming) was supposed to be exogenous to the recommendation process. I would like to study the interaction between recommender policy and the quality of the provided service. I build a model in which the firm is operating on the platform and provides customers with the service of ex-ante unknown quality. The firm can make a private and costly investment to increase the quality. The platform observes agents’ experience and commits to recommendation policy. The model proposes a new perspective on the role of the recommender system. Apart from inducing exploration, here the system can also encourage the firm to invest in quality as well as can smooth negative shocks.
	\end{abstract}
	\newpage
	\section{Introduction}
	Suppose you came to New-York and would like to find a good restaurant to go out tonight. Or you are going to spend your upcoming vacation on the coast of Spain and you need to find a hotel. What would you do? Where would you search for?  Before the World Wide Web, people in such cases relied upon guide-books and brochures distributed by traveling agents. Those guides usually quickly became out-of-dated and were criticized for containing a misleading information.

@@

	Papanstasiou et al. \cite{papanastasiou2017} extended ideas developed in \cite{kremer2014} and \cite{che2015}, and build a dynamic, stochastic model. In their model, agents also arrive sequentially to the platform and should choose between two alternatives that generate stochastically exogenous payoff. The platform in the paper designs a recommendation policy. Although the optimal policy turns out to have a complicated form, authors demonstrate that in this case the full revelation policy is not the best one, and the optimal policy involves information obfuscation.

@@

 	\begin{assumption}
 		If the good is not recommended to the customer, then the customer does not consume it. While if the good is recommended the customer may or may not choose it.
 	\end{assumption}
 	This assumption implies that without the platform the customer is unable to find the good. Think about \textit{TripAdvisor}, if it does not show you a restaurant, you will not know about the existence of this restaurant. At the same time, if \textit{TripAdvisor} shows you an option it is up to you whether to go there or not. 
\section{Analysis}
Although the recommender policy the platform employs can be a complicated function of all previous states, I start the analysis from the simplest policy. Namely, I firstly consider the policy that takes into account only the previous realization of the quality of the good. Moreover, in the following subsection I assume that the customers blindly follow the recommendation the platform makes.
\subsection{Nonstrategic customers}
Suppose that the platform employs the recommender policy that is based only on the previous period realization of the quality of the good. In this case the policy consists of two shares $\{s^0, s^1\}$ such that $$s_t = \begin{cases}
s^0, \text{ if }\mathcal{Q}_{t-1} = b\\
s^1, \text{ if }\mathcal{Q}_{t-1} = g
\end{cases}$$
The platform should choose $s^0, s^1$ to maximize its objective taking into account incentives of the firm. But firstly as a benchmark consider the first-best case, when the firm always invest. In this case the recommender policy is characterized by the following lemma

@@

	The firm exerts effort at bad state if and only if $$\delta V_{bb} \le \delta p V_{gb} + \delta (1-p)V_{bb} - c \iff V_{gb} - V_{bb} \ge \frac{c}{\delta p}$$
	Similarly, the firm exerts effort at good state if and only if $$V_{gg} - V_{bg} \ge \frac{c}{\delta p}$$ Suppose that the firm exerts effort at bad state, by way of contradiction assume that the firm does not invest at good state. In this case the system of equation becomes
	$$	\begin{cases}
	V_{bb} = \mathcal{P}s^0 + \delta p V_{gb} + \delta (1-p)V_{bb} - c\\
	V_{bg} = \mathcal{P}s^1 + \delta p V_{gb} + \delta (1-p)V_{bb} - c\\
	V_{gb} = \mathcal{P}s^0 + \delta V_{bg}\\
	V_{gg} = \mathcal{P}s^1 + \delta V_{bg}
	\end{cases}$$ and the solution is $$\begin{cases}
	V_{bb} = \frac{1+\delta p - \delta^2p}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 + \frac{\delta^2 p}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c}{(1-\delta)(1+\delta p)}\\
	V_{bg} = \frac{\delta}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 + \frac{1-\delta + \delta p}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c}{(1-\delta)(1+\delta p)}\\
	V_{gb} = \frac{(1+\delta p)(1-\delta)+\delta^2}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 - \frac{\delta^2(1-p)}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c \delta}{(1-\delta)(1+\delta p)}\\
	V_{gg} = \frac{\delta^2}{(1-\delta)(1+\delta p)}\mathcal{P}s^0 + \frac{1 - \delta^2 + \delta p}{(1-\delta)(1+\delta p)}\mathcal{P}s^1 - \frac{c\delta}{(1-\delta)(1+\delta p)}
	\end{cases}$$
	the condition that the firm invest at bad state is
	$$V_{gb} - V_{bb} = \frac{\delta\mathcal{P}}{1+\delta p}(s^1 - s^0) + \frac{c}{1+\delta p} \ge \frac{c}{\delta p}$$
	But this implies
	$$\frac{c}{\delta p} \le \frac{\delta\mathcal{P}}{1 + \delta p}(s^1 - s^0) + \frac{c}{1 + \delta p} = V_{gg} - V_{bg}$$ and hence it is also optimal to invest at good state. The contradiction demonstrates that if the firm invests at the bad state, it also invest at a good state. Using the similar argument it can be shown that investing at the good state also must imply investment at the bad state.
\end{proof}
The result means that either the firm invests at both states or does not invest at all.
The next proposition characterize the policy that induce the firm to invest in quality.
\begin{proposition}\label{prop1}
	Given the recommender policy $\{s^0, s^1\}$, the firm exerts effort at both states if and only if $$s^1 - s^0 \ge \frac{c}{\delta^2 p \mathcal{P}}$$
\end{proposition}
\begin{proof}
	Suppose the firm does not invest at all, in this case the system \eqref{eq1} becomes
	\begin{align*}
	\begin{cases}
	V_{bb} = \mathcal{P}s^0 + \delta V_{bb}\\
	V_{bg} = \mathcal{P}s^1 + \delta V_{bb}\\
	V_{gb} = \mathcal{P}s^0 + \delta V_{bg}\\
	V_{gg} = \mathcal{P}s^1 + \delta V_{bg}
	\end{cases} \to \begin{cases}
	V_{bb} = \frac{\mathcal{P}s^0}{1-\delta}\\
	V_{bg} = \mathcal{P}s^1 +\frac{\delta}{1-\delta}s^0\\
	V_{gb} = \delta \mathcal{P}s^1 + \frac{1-\delta + \delta^2}{1-\delta}\mathcal{P}s^0\\
	V_{gg} = (1+\delta)\mathcal{P}s^1 + \frac{\delta^2}{1-\delta}\mathcal{P}s^0
	\end{cases}
	\end{align*}
	The necessary condition that ensures that the firm does not invest is $	V_{gb} - V_{bb} < \frac{c}{\delta p}$. Here, $$	V_{gb} - V_{bb} = \delta \mathcal{P}(s^1 - s^0)$$ Hence, the firm will not invest if $s^1 - s^0 < \frac{c}{\delta^2 p \mathcal{P}}$.

	Now suppose, the firm invests in both states. In this case the system \eqref{eq1} becomes
	\begin{align*}
	\begin{cases}
	V_{bb} = \mathcal{P}s^0 + \delta p V_{gb} + \delta(1-p)V_{bb} - c\\
	V_{bg} = \mathcal{P}s^1 + \delta p V_{gb} + \delta(1-p)V_{bb} - c\\
	V_{gb} = \mathcal{P}s^0 + \delta pV_{gg} + \delta(1-p)V_{bg} - c\\
	V_{gg} = \mathcal{P}s^1 + \delta p V_{gg} + \delta (1 - p)V_{bg} - c
	\end{cases}
	\end{align*}
	It is a system of linear equations, and its solution is given by:
	$$\begin{cases}
	V_{bb} = \frac{\delta^2p}{1-\delta}\mathcal{P}s^1 + \frac{1-\delta^2p}{1-\delta}\mathcal{P}s^0 - \frac{c}{1-\delta}\\
	V_{bg} = \frac{1-\delta + \delta^2p}{1-\delta}\mathcal{P}s^1 + \frac{\delta(1-\delta p)}{1-\delta}\mathcal{P}s^0 - \frac{c}{1-\delta}\\
	V_{gb} = \frac{\delta(1-\delta+\delta p)}{1-\delta}\mathcal{P}s^1 + \frac{1-\delta + \delta^2 - \delta^2 p}{1- \delta}\mathcal{P}s^0 - \frac{c}{1-\delta}\\
	V_{gg} = \frac{1 - \delta^2 + \delta^2 p}{1 - \delta}\mathcal{P}s^1 + \frac{\delta^2(1-p)}{1- \delta}\mathcal{P}s^0 - \frac{c}{1 - \delta}
	\end{cases}$$
	and again to ensure that the firm indeed invests one needs to check that $V_{gb} - V_{bb} \ge \frac{c}{\delta p}$. In this case $$V_{gb} - V_{bb} = \delta\mathcal{P}(s^1 - s^0) \ge \frac{c}{\delta p} \iff s^1 - s^0 \ge \frac{c}{\delta^2 p \mathcal{P}}$$
\end{proof}
The result means that the difference in demand of customers that the platform provides the firm with should be high enough to make it optimal for the firm to invest in quality. Also, the straightforward corollary can be obtained
\begin{corollary}
	It is possible to incentivize the firm to invest only if $c \le \delta^2 p \mathcal{P}$.
\end{corollary}
Thereafter I will assume that the condition above condition holds.
\begin{corollary}
	It becomes harder to encourage firm to invest if either cost of investment $c$ is high, or the probability that investment results in quality increase $p$ is low, or the discount factor $\delta$ is low, ot the priced paid by customers $\mathcal{P}$ is low.
\end{corollary}

The next step is to choose the policy $\{s^0, s^1\}$ to maximize the platform's utility subject to the constraint imposed by the Proposition \ref{prop1}. The following theorem characterize the optimal one-round recommender policy.
\begin{theorem} \label{th1}
	If it is optimal to encourage the firm to invest, then the optimal one-round recommender policy is characterized by $\{s^1, s^0\}$ such that:
	\begin{itemize}
		\item if $p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}} < 0$ then $\left\{s^0 = 0, s^1 = \frac{c}{\delta^2 p \mathcal{P}} \right\}$
		\item if $p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}} \ge 0$ then
		\begin{itemize}
			\item if $p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}} < 1$ then $$\begin{cases}s^0 = p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}}\\ s^1 = p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}} \end{cases}$$
			\item if $p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}} \ge 1$ then $\left\{s^0 = 1-\frac{c}{\delta^2 p \mathcal{P}}, s^1 =1 \right\}$
		\end{itemize}
	\end{itemize}
\end{theorem} 
\begin{proof}
	Let $U_i$ be the expected discounted value of the platform if the state of the firm in the previous period was $i$. Then these values are solutions to the following system of equations. 
	\begin{align*}
	&\begin{cases}
	U_b = p\left((1-\mathcal{P})s^0 - \frac{(s^0)^2}{2} + \delta U_g\right) + (1-p)\left((q - \mathcal{P})s^0 - \frac{(s^0)^2}{2} + \delta U_b \right)\\
	U_g = p\left((1- \mathcal{P})s^1 - \frac{(s^1)^2}{2} + \delta U_g\right) + (1-p)\left((q - \mathcal{P})s^1 - \frac{(s^1)^2}{2} + \delta U_b \right)
	\end{cases} 
	\end{align*}
	which can be rewritten as
	\begin{align*}
	\begin{cases}
	U_b = \frac{1}{1 - \delta(1-p)} \left( (p + (1-p)q - \mathcal{P})s^0 - \frac{(s^0)^2}{2} \right) + \frac{p\delta}{1 - \delta(1-p)}U_g\\
	U_g = \frac{1}{1 - \delta p} \left( (p + (1-p)q - \mathcal{P})s^1 - \frac{(s^1)^2}{2} \right) + \frac{(1-p)\delta}{1 - \delta p}U_b
	\end{cases}
	\end{align*}
	the solution is given by
	$$\begin{cases}
	U_b = \frac{1-\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^0 - \frac{(s^0)^2}{2}\right) + \frac{\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^1 - \frac{(s^1)^2}{2}\right)\\
	U_g = \frac{\delta (1-p)}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^0 - \frac{(s^0)^2}{2}\right) +\frac{1-\delta(1- p)}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^1 - \frac{(s^1)^2}{2}\right)
	\end{cases}$$
	without loss of generality suppose that at $t = 0$ the firm is at bad state and the platform knows it. Then the platform should solve the following problem
	\begin{align*}
	\underset{s^1, s^0}{\max}&\ \frac{1-\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^0 - \frac{(s^0)^2}{2}\right) + \frac{\delta p}{1-\delta}\left((p + q(1-p) - \mathcal{P})s^1 - \frac{(s^1)^2}{2}\right)
	\end{align*}
	Clearly $s^1 - s^0 \ge \frac{c}{\delta^2 p \mathcal{P}}$ should bind. Suppose that $s^1 < 1$, we can plug $s^0 = s^1 - \frac{c}{\delta^2 p \mathcal{P}}$ into the objective function. In this case the optimal solution is given by \begin{align}\label{eq2}
	s^0 &= p + q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} \nonumber\\
	s^1 &= p + q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}}
	\end{align}
	Keeping in mind that $s^0 = s^1 - \frac{c}{\delta^2 p \mathcal{P}}$ the objective function is a downward parabola, hence, if $p+q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} < 0$ (and using the assumption that $\frac{c}{\delta^2 p \mathcal{P}} < 1$) then $s^0 = 0$ and to keep the constraint that ensures that the firm exerts effort satisfied, $s^1 = \frac{c}{\delta^2 p \mathcal{P}}$. If $p+q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} \ge 0$ then two cases are possible: either $p+q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}} < 1$ or $p+q(1-p) - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}} \ge 1$. The former case implies an internal solution and $$\begin{cases}s^0 = p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}}\\ s^1 = p+(1-p)q - \mathcal{P} - \frac{c}{\delta \mathcal{P}} + \frac{c}{\delta^2 p \mathcal{P}} \end{cases}$$
	The latter case implies $s^1 = 1$ and consequently $s^0 = 1 - \frac{c}{\delta^2 p \mathcal{P}}$.
\end{proof}
